At a global scale, conservation of pollinators and herbivores between related plants varies widely across communities and between plant families - Supporting Information

### 2019-12-09 manuscript/supporting_info.tex
trying to be nicer to the idiot reviewer

\section*{Supporting information 2: Repeating our analyses with proportion of shared partners}

@@

\section*{Supporting information 3: Distributions of $p$-values for permuted networks}

@@

\section*{Supporting information 4: Details of within-family regressions}

>>>>

\section*{Supporting information 2: R implementation of tuple-form regression}

    We first fit a series of regressions (one per network) relating the Jaccard dissimilarity of the interaction partners of plants $i$ and $j$ ($J_{ij}$) to the phylogenetic  distance between them ($\delta_{ij}$), using the form
    %
      \begin{equation}
        {\rm logit}\left(J_{ij}\right) \propto \beta_{distance}\delta_{ij} .
        \label{basic}
      \end{equation}
    %
    We fit these regressions using the R~\citep{R} base function ``glm'', which will accept $J_{ij}$ formatted as either a single value summarizing the probability of sharing an interaction partner \emph{or} the numbers of shared and un-shared interaction partners ($M_{ij}$ and $U_{ij}$). As we wished to use the tuple ($M_{ij}$, $U_{ij}$) as our input, the command in R was:

    \emph{model=glm(cbind(M\_ij,U\_ij) $\sim$ scale(delta\_ij),family="binomial")}.

    We used the same tuple-input form of the binomial regression for all subsequent regressions.

\section*{Supporting information 3: Repeating our analyses with proportion of shared partners}

@@

\section*{Supporting information 4: Distributions of $p$-values for permuted networks}

@@

\section*{Supporting information 5: Details of within-family regressions}
